\ifx allfiles undefined
\documentclass{article}
\usepackage{CJK}
\usepackage{verbatim}

%%%代码
\usepackage{color}
\usepackage{xcolor}
\definecolor{keywordcolor}{rgb}{0.8,0.1,0.5}
\usepackage{listings}
\lstset{breaklines}%这条命令可以让LaTeX自动将长的代码行换行排版
\lstset{extendedchars=false}%这一条命令可以解决代码跨页时，章节标题，页眉等汉字不显示的问题
\lstset{language=C++, %用于设置语言为C++
    keywordstyle=\color{keywordcolor} \bfseries, %设置关键词
    identifierstyle=,
    basicstyle=\ttfamily, 
    commentstyle=\color{blue} \textit,
    stringstyle=\ttfamily, 
    showstringspaces=false,
    %frame=shadowbox, %边框
    captionpos=b
}
%%%

%\hypersetup{CJKbookmarks=true} %解决section不能使用中文的问题

\begin{document}
\begin{CJK}{UTF8}{gbsn}     %CJK:支持中文

\else
    
\begin{description}
    \item{\textbf{问题}}: Implement atoi to convert a string to an integer. \textit{(leetcode 8)}
	\item{\textbf{Note}}: The function first discards as many whitespace characters as necessary until the first non-whitespace character is found. Then, starting from this character, takes an optional initial plus or minus sign followed by as many numerical digits as possible, and interprets them as a numerical value.

The string can contain additional characters after those that form the integral number, which are ignored and have no effect on the behavior of this function.

If the first sequence of non-whitespace characters in str is not a valid integral number, or if no such sequence exists because either str is empty or it contains only whitespace characters, no conversion is performed.

If no valid conversion could be performed, a zero value is returned. If the correct value is out of the range of representable values, INT\_MAX (2147483647) or INT\_MIN (-2147483648) is returned.
    \item{\textbf{Care}} : \fbox{时间复杂度O(n), 空间复杂度O(1)}
    \\这个问题主要要注意两个方面,一个是空格和非法字符,一个是溢出,空格和非法字符都很好处理,溢出的处理方式就值得去研究,在C++中INT\_MAX的绝对值比INT\_MIN小1,所以负数个数比正数个数多一个,你可以都转化位负数来判断溢出. 当然,对付溢出还有一种偷懒的方法就是使用double类型取存储数据.
    \begin{lstlisting}
int atoi(const char *str){
	int sum = 0;  // 存负值.
	bool isMinus = false;
	const char* p = str;
	if(!p)	return 0;
	while(*p == ' ' && *p != '\0') p++; //空格
	if(*p == '\0')	return 0;
	if(*p == '-'){
		isMinus = true;
		p++;
	}else{
		if(*p == '+') p++;
	}
	while(*p != '\0'){
		int cur = *p++ - '0';
		if(!(cur >= 0 && cur <= 9))	break;  //非法字符
		if(isMinus && sum == INT_MIN/10 && cur > INT_MAX%10 + 1){
			return INT_MIN;
		}
		if(isMinus && sum < INT_MIN/10){
			return INT_MIN;
		}
		if(!isMinus && sum == -INT_MAX/10 && cur > INT_MAX%10){
			return INT_MAX;
		}
		if(!isMinus && sum < -INT_MAX/10){
			return INT_MAX;
		}
		sum = sum*10 - cur;
	}
	if(!isMinus)	return -sum;
	return sum;
}
    \end{lstlisting}
\end{description}

\fi

\ifx allfiles undefined
\end{CJK}
\end{document}
\fi
